%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Prima Assicurazioni S.p.A} % Organization
    {Milan, Italy} % Location
    {Nov. 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on the core Claims Management system, written in Elixir and Elm, which hosts hundreds of thousands of claims.}
        \item {Developed libraries, microservices and services in either Elixir or Rust, to support the internal claims department with third-party integrations: regulatory entities, bank payments systems, physical mail delivery services.}
        \item {Developed a service in Rust and React to allow external car body repair shops to handle their appointments and help them interact with the internal claims department.}
        \item {Set up message queues for asynchronous processing of messages using RabbitMQ, and used them to feed data into Redshift and other Business Intelligence tools.}
        \item {Worked on the Datadog integration to help collect infrastructure and business metrics, and implemented distributed tracing using the OpenTelemetry standard.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer Consultant @ Bank} % Job title
    {Banca Popolare di Puglia e Basilicata} % Organization
    {Altamura, Italy} % Location
    {May. 2018 - Nov. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Gathered business requirements to help an enterprise organization transition to a software-based HelpDesk and Knowledge Base system.}
        \item {Implemented a tailor-made solution for the client that involved the development of several C\# modules, used both for frontend interactions as well as for application analytics.}
        \item {Deployed said solution on the client' on-premises infrastructure, along with custom modules for performing SSO.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer Consultant @ LegalTech startup} % Job title
    {Law Engineering Systems} % Organization
    {Siena, Italy} % Location
    {Nov. 2017 - May. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented a frontend in Javascript aimed at visualizing different versions of the same law, in a git-like fashion.}
        \item {Implemented backend services to gather legal data and expose it to the frontend using an API, made with Django and GraphQL.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Curricular Internship} % Job title
    {Scloby} % Organization
    {Turin, Italy} % Location
    {Apr. 2015 - Jul. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented E2E tests for an application built with Javascript and Cordova, which ran on tablets used by customers to handle their shop' orders, stock, and so on.}
        \item {Worked on several sections of the AngularJS frontend to add features and perform bug fixes.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
